\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly

### 2014-10-01 paper.tex
Integrated most of Julia 'little things' + a few from Pierre

\title{\LARGE \bf
How Children Perceive and Interact with a Robot that Behaves Unexpectedly -- The Domino Experiment
}

@@

\begin{document}
\maketitle
\begin{abstract}

@@

While we found only a limited recognition of the different misbehaviours of the
robot that we attribute to the age of the subject (M=4.46), interesting findings
include a sustained engagement level, an unexpectedly low level of attribution
of higher cognitive abilities and a \emph{negative} correlation between
anthropomorphic projections and actual behavioural engagement.

Besides, this study operationalizes for the first time the
\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which proves a
valuable tool to assess qualitative psycho-behavioural episodes occurring during
human-robot interaction.

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Towards Sustained Engagement}

@@

Different possibilities to foster engagement (both short- and long-term
engagement) in HRI have been explored, in particular with social robots. A lot
of research has moved toward creating sophisticated emotional models which cause
complex robot behaviour. \cite{leite_long-term_2013} studied the long-term
engagement of children with a chess playing robot that adapted its behaviour to
the children and showed empathy toward them. She found that empathetic robots
are more likely to engage users in the long-term and they proposed several
guidelines for designing such artificial companions. Other works
\cite{bickmore_maintaining_2010,short_no_2010} have shown that simpler ways to
enhance engagement may as well be effective.

@@

Similarly, looking at short-term engagement, \cite{short_no_2010} found that a
simple manipulation of the robot's behaviour can lead to greater engagement. The
authors let participants play several rounds of the rock-paper-scissors game
with the robot (the playfulness of the scenario seems important). When the robot
was cheating from time to time, participants tended to ascribe intention to the
robot what in turn led to greater engagement in how they were interacting with
the robot. The authors observe that \textit{``any deviation from expected
operation is sufficient to create a greater degree of engagement in the
interaction.''} Besides, they suggest that \textit{``many interactions can be
improved by the introduction of such simple behaviours, and that this should
be exploited by designers in HRI. Bringing human and robot together to
perform a simple, repetitive, familiar task and then having the robot behave
unexpectedly can increase engagement and mental state attribution without
complex behavioural or mechanical additions.''}.  Along those lines, Fink
\etal\cite{fink2014dynamics} also suggest in their model of the dynamics of
anthropomorphism, that \emph{disruptive behaviours} may lead to increased
anthropomorphic projections and possibly engagement.

Based on these previous researches, we would like to find out in this study how
we can enhance children's experience with the robot so that they do not find it
repetitive and boring, and ultimately keep interacting with the robot (as
repetitiveness is likely to decrease a user's motivation to continue using a
system~\cite{bickmore_establishing_2005}).

@@

    \item The robot gets \textbf{lost}: When called by the child to come over,
        the robot goes wrong, without any observable reason, and remains at the
        wrong location. We expect this to be perceived as a mechanical
        malfunction (a bug or system error which causes the robot to not work
        correctly), and hypothesize decreased attributions of human-likeness to
        the robot.\footnote{We use interchangeably \textit{attribution of
            human-likeness} and \textit{anthropomorphic projections} in the
        remaining of the article.}

    \item The robot \textbf{disobey}: When called by the child to come over, the
        robot shows it refuses to obey by literally ``shaking its head'' and
        becoming red. The robot then goes to a wrong location and remains there
        while it continues to shake its head. We expect the disobey behaviour to
        be perceived as the robot having an explicit \textit{``own will''}, and
        we assume this leads to increased attributions of human-likeness
        (ascribing intentionality) to the robot.

    \item The robot makes a \textbf{mistake}: When called by the child to come
        over, the robot goes wrong but recognizes its mistake and repairs. We
        expect this to be perceived (explicitly) as \textit{``to err is
        human''}, and (implicitly) as the robot being endowed with a certain
        level of introspective capabilities (it was able to recognize its own
        error). In this condition, we assume increased attributions of
        human-likeness to the robot.

@@

    \item[Hypothesis 2:] Children perceive a robot that (tentatively) displays
        intention or cognitive abilities as more human-like than a robot that
        appears to have a system error, \ie the disobeying robot and the robot
        that makes a mistake will be more anthropomorphized than the robot that
        gets lost (between subjects variable).

@@

Our research questions deal with both children's observable behaviour and their
perception of the robot. We would also like to explore the relation between
these two aspects, related to the attribution of human-like characteristics to
the robot. The motivation behind this is to find out whether
\textit{anthropomorphism} can not only be measured as a specific type of
perception but also as an observable behaviour in the interaction itself. Thus,
we would like to bridge things together and, relying on the concept of
anthropomorphism index~\cite{fink2014dynamics}, build a compound metric that
considers both children's perception and interaction aspects (qualitatively).
Previous work suggests that a social relation to a robot (we view
anthropomorphism as a specific type of social relation) reflects an increased
engagement and can be effective in sustaining interaction.  Consequently, we
formulate a third hypothesis:

@@

\subsection{Scenario and course of the study}

\subsubsection{Experimental setting}

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed (displayed as black
        stars). A playground with a river drawn on it is used as an imaginary
        barrier that only the robot is allowed to cross. The solid green arrows
        show the robot's path for the \textit{correct} behaviour. The blue
        dashed arrow visualizes a possible \textit{lost} path, where the Ranger
        stops and remains at a wrong stop. The yellow arrows reflect a possible
        \textit{mistake} path, where the robot goes wrong but then turns back
        and goes to the child. The red dashed arrow visualizes a possible
        \textit{disobey} path where the robot goes wrong, then turns toward the
        child but stays at a wrong position.}

@@

The interaction scenario consisted in two children who play domino together,
with the help of the robotic box Ranger. The scenario setup is displayed in
Figure~\ref{fig:domino-setup}. The challenge is that the tiles of the domino are
distributed in the room, hidden behind three beanbags, and while one child --
\textit{the searcher} -- searches for the right tile, the other child --
\textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
(playground) in between the two children that we told them they cannot cross
and therefore they need the robot to transport the domino tiles between them.

@@

The game (divided in several \emph{runs} that correspond each to the delivery
and assembling of one domino tile) starts with one domino tile in front of the
tent, where the receiver child stays and assembles the domino chain. The
receiver child asks the searcher child for a specific tile, \eg a tile with a
donkey, the searcher searches for the respective tile, sits down on the next
beanbag, and asks the robot to come over.  The Ranger robot is first located
next to the tent, then, when called by the searcher (\textit{``Robot, come
here!''}), it starts moving, crosses the river carpet, and comes over to the
searcher on the beanbag. The searcher child puts the domino tile into the
robotic box, and the robot then goes back to the receiver child in the tent.
Then, the receiver takes out the domino tile from the robot, and puts the two
tiles together. The first \emph{run} is over, and a new \emph{run} starts, when
the receiver asks the searcher for the next domino tile.

@@

Overall, there were 13 pairs of children (n=26) participating in the interaction
study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
French-speaking. In 11 of the pairs, children were friends who knew each other
from kindergarten, nursery school or because they lived in the same
neighbourhood. 2 of the pairs were composed of brother and sister.

\subsubsection{Course of the study}

In our study, there were a total of 14 runs, and at each run, the robot exhibits
one out of four possible behaviours: \emph{correct}, \emph{lost}
\emph{disobey} or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles and in the 9 remaining runs (\emph{2.1} to \emph{2.9}), the robot
showed one of the misbehaviour (\emph{lost}, \emph{disobey} or \emph{mistake})
at the $3^{rd}$ and $4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run
(see Figure~\ref{fig:domino-time-active}). The study is build as a
between-subject study, and the type of misbehaviour was therefore always the
same for a given group.

Special attention has been paid to the distribution of misbehaving runs during
the study. The five first correct runs aims at setting the children expectation
regarding a consistent robot behaviour. When the robot then exhibits an
unexpected behaviour, children are likely to be positively surprised (a similar
effect has been observed in a study with a robot that was cheating from time to
time~\cite{short_no_2010}).  Besides, to prevent the robot misbehaviours to be
immediately interpreted as failures, we introduce these misbehaviour neither at
the very beginning nor at very end of the interaction
(\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
failures negatively impact trust. \cite{short_no_2010} also adopted a similar
pattern when introducing unexpected robot behaviour).

\begin{figure}[!t]
    \centering
    \subfloat[lost]{
        \label{fig:domino-lost}
        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
    }
    \subfloat[disobey]{
        \label{fig:domino-disobey}
        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
    }
    \subfloat[mistake]{
        \label{fig:domino-mistake}
        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
    }
    \caption{\small The three robot misbehaviours.}
    \label{fig:domino-misbehaviour}
\end{figure}

@@

    \item \textbf{Lost:} After being called, Ranger goes until it is on the
    carpet. There, it stops, turns, and goes wrong (see blue path in
    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
    with its ``face'' turned away from the child, and it blinks in yellow light,
    as if it was in front of a child. Ranger remains waiting at the wrong
    position until the experimenter tells the child to go over to the robot to
    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
    as it needs human-intervention.

    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
    carpet. It then stops, makes red
    light all over its surface and produces a repeated ``disturbance'' sound. It
    turns, and goes to a wrong position (see red path in
    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
    toward the sender child. In addition to the red blinking, Ranger
    makes a slow wiggle-like move, and remains waiting at the wrong position
    until the experimenter tells the child to go over to the robot to put the
    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.

    \item \textbf{Mistake:} The sender child calls Ranger. The robot goes until
    it is on the carpet, stops, turns, and goes wrong (see yellow path in
    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
    ``face'' toward the sender child, and ``blushes'' red around its ``cheeks''
    (as if it recognizes its wrong position) and finally goes correctly over to
    the sender child. The \textit{mistake} behaviour is \textit{robot-repaired},
    as no human-intervention is needed.

@@

On its way back to the tent, Ranger always goes correctly. After the sender
child has put a domino tile, Ranger automatically turns and goes over to the
tent (the receiver child does not need to call the robot). The receiver child
takes the tile and the robot moves to a waiting location until the next run
starts.

\subsection{Data collection}

We have obtained and analysed two types of data. The \textbf{children's
behaviours toward the robot} (\ie the child-robot interactions) have been
captured in the video recordings by annotating a set of actions, described
below. The children's \textbf{phenomenological perception of the robot} has been
captured through two audio-recorded semi-structured interviews which took place
between run \emph{1.5} and \emph{2.1} and at the end of the 14 runs.

\subsubsection{Interaction: Action coding}

@@

We annotated children's behaviour in the video records, and coded 10 different
actions: \textbf{explore} (actively try to find out what the robot is doing, \eg
by looking under the box; attentively watch or observe the robot; experiment
with the robot to figure out how it works); \textbf{misuse} (kick the robot,
poke it in its ``eye'', try to climb on or inside the box, drive/push the robot
around, stop the robot's wheels with a foot); \textbf{put} (a domino tile is put
inside the box); \textbf{remove} (a domino tile is removed from the box);
\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
petted or caressed); \textbf{show} (show something to the robot; \textbf{call}
(call the robot to come over); \textbf{talk} (all the other case of direct
verbal interaction); \textbf{look} (when a child looks \emph{at the
experimenter} due to confusion caused by the robot; look is not coded when the
experimenter asks a question to the child);

@@

The actions \textit{put, remove} and \textit{call} were ``requested'' actions
that the children had to perform in the scenario. On the contrary,
\textit{explore, misuse, gesture, touch, show, talk} and \textit{look} are
spontaneous actions that were not requested but arose in the interaction.  These
actions reflect engagement, and are the one we considered during the analysis.
Figure~\ref{fig:domino-time-active} shows the distribution of these actions over
the different runs, in summed over the three condition.

\subsubsection{Phenomenological perception: semi-structured interviews}

One pre-interview and two interviews (between run \emph{1.5} and \emph{2.1} and
at the end) were conducted with the children.  We set up the interviews like a
casual conversation / discussion, so we did not separate the two children in
order to keep the situation natural. We used casual and informal language
adapted to the age of the children, and encouraged them to justify their answers
and tell us more details by asking, for example, \textit{How do you know ... ?}
or \textit{Tell me, what have you observed when ... ?}. We paid attention to not
``put words in children's mouth''. Consequently, though we re-phrased and
repeated some questions, we never forced children to give an answer, and
accepted when they said they would not know or when they did not respond at all.

@@

In designing our interview script and selecting relevant questions, we took
inspiration from previous work on child-robot interaction and children's
perception of robots
\cite{kahn_jr._robotic_2006,weiss_i_2009,leite_influence_2013}. For instance, we
applied and adapted some of the \emph{constructs} and example questions from the
questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. A
\emph{construct} addresses a specific factor (topic) that can be measured by
several questions. For instance, the construct ``cognitive connections'' (using
Flavell's terminology~\cite{flavell1988development}) considers the robot's
ability to hear and to see (perceptual skills), as attributed by the children.
The construct ``moral standing'' and the related question was taken from
\cite{kahn_jr._robotic_2006}.\footnote{According to
\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based
on an artifact's physical or psychological welfare, and virtue (whether the
artifact deserves care). An attribution of moral standing reflects, for
instance, that the robot engenders moral regard, is morally responsible,
blameworthy, has rights or deserves respect.} Similarly, we grouped
questions according to specific constructs that they evaluate (see
Table~\ref{tab:domino-questions}).

@@

    \item Other \textbf{anthropomorphic statements}: \textit{1 point} for anthropomorphic
        reason for Ranger's misbehaviour; \textit{2 points} for anthropomorphic reason
        for not leaving Ranger alone.

@@

\subsection{Misbehaviour recognition and engagement}

As stated in the introduction, we had hypothesized that the \textit{disobey}
behaviour is perceived as the robot intentionally not doing what it should do.
The \textit{mistake} behaviour was intended to show that the robot can do a
mistake but is aware of it and able to repair its mistake, which should also
lead to the perception of intentionality and introspective skills.  Contrary, we expected that the
\textit{lost} condition is perceived as a malfunction or bug of the robot.  In
the second interview, after the robot had misbehaved, we asked children whether
the robot always did what they wanted it to do. Most children disagreed and said
they noticed something strange.
%However, there were some children who gave a
%positive answer, suggesting that they found the robot always did what they
%wanted it to do. This was a surprise. Had they not noticed the robot's
%misbehaviour? Why not? On one hand, we found that children sometimes gave
%contradictory replies when asked the same question twice. This is difficult to
%interpret. On the other hand, children may have a general tendency to please
%adults \cite{leite_long-term_2013}, and it could be the case that some were too
%shy to tell us that the robot did something strange.

@@

When asked why they thought the robot had not always come
over to them, 4 of the children did not reply. The remaining ones gave a variety
of reasons (Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9
of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
is doing and that it could go \textit{no matter where}\footnote{We translated
children's answers from French to English. For some expressions the meaning
and connotation of an expression may not be the same. We understand
\textit{``partir dans tous les sens''} as ``to go off in all possible
directions'' and hence interpret this reflects viewing the robot as being
unpredictable.} because \textit{``with robots you have these kind of problems,
they do no matter what''}. 8 replies related to \textit{technical problems}
(including \textit{broken parts}), suggesting that children perceived the
misbehaviour as unintended by the robot. 2 of the children who had interacted
with the disobeying robot said Ranger was \textit{angry}, which none of the
children in other conditions replied. Several children ascribed intentionality
to Ranger explaining that it \textit{did not want to continue} carrying domino
tiles or that it \textit{made a mistake / did something silly}\footnote{We
understood \textit{``faire une bêtise''} as ``to do a silly thing'' in the sense
of making a mistake.}.

@@

In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
here. The findings here do not directly address the issues
of long-term usage but concern short-term \textit{engagement}, which is a
pre-requisite for long-term usage.

>>>>

\title{\LARGE \bf
How Children Perceive and Interact with a Robot that Behaves Unexpectedly
}

@@

\begin{document}
\sloppy % prevent margin overflow
\maketitle
\begin{abstract}

@@

While we found only a limited recognition of the different misbehaviours of the
robot that we attribute to the age of the child participants (M=4.46),
interesting findings include a sustained engagement level, an unexpectedly low
level of attribution of higher cognitive abilities and a \emph{negative}
correlation between anthropomorphic projections and actual behavioural
engagement.

Besides, this study operationalizes for the first time the
\emph{anthropomorphism index} proposed by~\cite{fink2014dynamics}, which can be
considered as an effective tool to assess qualitative psycho-behavioural
episodes occurring during human-robot interaction.

\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Towards Engagement}

@@

Different possibilities to foster engagement (both short- and long-term
engagement) in HRI have been explored, in particular with social robots. A lot
of research has moved toward creating sophisticated emotional models which cause
complex robot behaviour. \cite{leite_long-term_2013} studied the long-term
engagement of children with a chess playing robot that adapted its behaviour to
the children and showed empathy toward them. The authors found that empathetic robots
are more likely to engage users in the long-term and they proposed several
guidelines for designing such artificial companions. Other works
\cite{bickmore_maintaining_2010,short_no_2010} have shown that simpler ways to
enhance engagement may as well be effective.

@@

Similarly, looking at short-term engagement, \cite{short_no_2010} found that a
simple manipulation of the robot's behaviour can lead to greater engagement. The
authors let participants play several rounds of the rock-paper-scissors game
with the robot (the playfulness of the scenario seems important). When the robot
was cheating from time to time, participants tended to ascribe intention to the
robot what in turn led to greater engagement in how they were interacting with
the robot. The authors observe that \textit{``any deviation from expected
operation is sufficient to create a greater degree of engagement in the
interaction.''} Besides, they suggest that \textit{``many interactions can be
improved by the introduction of such simple behaviours, and that this should
be exploited by designers in HRI. Bringing human and robot together to
perform a simple, repetitive, familiar task and then having the robot behave
unexpectedly can increase engagement and mental state attribution without
complex behavioural or mechanical additions.''}  Along those lines, Fink
\etal\cite{fink2014dynamics} also suggest in their model of the dynamics of
anthropomorphism in HRI, that \emph{disruptive behaviours} may lead to increased
anthropomorphic projections and possibly engagement.

Based on this previous research, we would like to explore in this study how
we can enhance children's experience with the robot so that they do not find it
repetitive and boring, and ultimately keep interacting with the robot (as
repetitiveness is likely to decrease a user's motivation to continue using a
system~\cite{bickmore_establishing_2005}).

@@

    \item The robot gets \textbf{lost}: When called by the child to come over,
        the robot goes wrong, without any observable reason, and remains at the
        wrong location. We expect this to be perceived as a mechanical
        malfunction (a bug or system error which causes the robot to not work
        correctly), and hypothesise decreased attributions of human-likeness to
        the robot.\footnote{We use interchangeably \textit{attribution of
            human-likeness} and \textit{anthropomorphic projections} in the
        remaining of the article.}

    \item The robot \textbf{disobeys}: When called by the child to come over, the
        robot shows that it refuses to obey by literally ``shaking its head'' and
        becoming red. The robot then goes to a wrong location and remains there
        while it continues to shake its head. We expect the disobey behaviour to
        be perceived as the robot having an explicit \textit{``own will''}, and
        we assume this leads to increased attributions of human-likeness
        (ascribing intentionality) to the robot.

    \item The robot makes a \textbf{mistake}: When called by the child to come
        over, the robot goes wrong but recognises its mistake and repairs. We
        expect this to be perceived (explicitly) as \textit{``to err is
        human''}, and (implicitly) as the robot being endowed with a certain
        level of introspective capabilities (it was able to recognise its own
        error). In this condition, we assume increased attributions of
        human-likeness to the robot.

@@

    \item[Hypothesis 2:] Children perceive a robot that (tentatively) displays
        intention or cognitive abilities as more human-like than a robot that
        appears to have a system error, \ie the disobeying robot and the robot
        that makes a mistake will be more anthropomorphised than the robot that
        gets lost (between subjects variable).

@@

Our research questions deal with both children's observable behaviour and their
perception of the robot. We would also like to explore the relation between
these two aspects, related to the attribution of human-like characteristics to
the robot. The motivation behind this is to find out whether
\textit{anthropomorphism} can not only be measured as a specific type of
perception but also as an observable behaviour in the interaction itself. Thus,
we would like to bring things together and, relying on the concept of
anthropomorphism index~\cite{fink2014dynamics}, build a compound metric that
considers both children's perception and interaction aspects (qualitatively).
Previous work suggests that a social relation to a robot (we view
anthropomorphism as a specific type of social relation) reflects an increased
engagement and can be effective in sustaining interaction.  Consequently, we
formulate a third hypothesis:

@@

\subsection{Scenario and Course of the Study}

\subsubsection{Experimental Setting}

\begin{figure}[ht!] 
    \centering 
    \includegraphics[width=0.9\columnwidth]{domino-setup.pdf} 
    \caption{\small \textbf{Experimental setting} One child is located in a
        tent, while the other is asked to sit on one of the three beanbags,
        behind each of which 3 domino tiles are distributed (displayed as black
        stars). A play mat with a river drawn on it is used as an imaginary
        barrier that only the robot is allowed to cross. The solid green arrows
        show the robot's path for the \textit{correct} behaviour. The blue
        dashed arrow visualises a possible \textit{lost} path, where the Ranger
        stops and remains at a wrong spot. The yellow arrows reflect a possible
        \textit{mistake} path, where the robot goes wrong but then turns back
        and goes to the child. The red dashed arrow visualises a possible
        \textit{disobey} path where the robot goes wrong, then turns toward the
        child but stays at a wrong position.}

@@

The interaction scenario consisted in two children who play domino together,
with the help of the robotic box Ranger. The scenario setup is displayed in
Figure~\ref{fig:domino-setup}. The challenge is that the tiles of the domino are
distributed in the room, hidden behind three beanbags, and while one child --
\textit{the searcher} -- searches for the right tile, the other child --
\textit{the receiver} -- is asked to stay in a play tent. There is a ``river''
(play mat) in between the two children that we told them they cannot cross
and therefore they need the robot to transport the domino tiles between them.

@@

The game (divided in several \emph{runs} that correspond each to the delivery
and assembling of one domino tile) starts with one domino tile in front of the
tent, where the receiver child stays and assembles the domino chain. The
receiver child asks the searcher child for a specific tile, \eg a tile with a
donkey, the searcher child searches for the respective tile, sits down on the next
beanbag, and asks the robot to come over.  The Ranger robot is first located
next to the tent, then, when called by the searcher (\textit{``Robot, come
here!''}), it starts moving, crosses the river carpet, and comes over to the
searcher on the beanbag. The searcher child puts the domino tile into the
robotic box, and the robot then goes back to the receiver child in the tent.
Then, the receiver takes out the domino tile from the robot, and puts the two
tiles together. The first \emph{run} is over, and a new \emph{run} starts, when
the receiver asks the searcher for the next domino tile.

@@

Overall, there were 13 pairs of children (n=26) participating in the interaction
study: 16 boys and 10 girls, 4-5 years old (M=4.46, SD=0.45), all
French-speaking. We based our age range choice on a previous study ``in the
wild''~\cite{fink2014which} that suggested that younger children (4-6 years)
interacted more effectively with the Ranger robot.

In 11 of the pairs, children were friends who knew each other
from kindergarten, nursery school or because they lived in the same
neighbourhood. 2 of the pairs were composed of brother and sister. One parent
would generally attend, sit on a chair behind the children.

\subsubsection{Course of the Study}

In our study, there were a total of 14 runs, and at each run, the robot exhibits
one out of four possible behaviours: \emph{correct}, \emph{lost} \emph{disobey}
or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles receiver/searcher and in the 9 remaining runs (\emph{2.1} to
\emph{2.9}), the robot showed one of the misbehaviours (\emph{lost},
\emph{disobey} or \emph{mistake}) at the $3^{rd}$ and $4^{th}$ run as well as at
the $7^{th}$ and $8^{th}$ run (see Figure~\ref{fig:domino-time-active}). The
study is built as a between-subject study, and the type of misbehaviour was
therefore always the same for a given group.

Special attention has been paid to the distribution of misbehaving runs during
the study. The five first correct runs aim at setting the children's expectation
regarding a consistent robot behaviour. When the robot then exhibits an
unexpected behaviour, children are likely to be positively surprised (a similar
effect has been observed in a study with a robot that was cheating from time to
time~\cite{short_no_2010}).  Besides, to prevent the robot misbehaviours to be
immediately interpreted as failures, we introduce these misbehaviours neither at
the very beginning nor at the very end of the interaction.
\cite{desai_effects_2012,desai_impact_2013} show that early and late robot
failures negatively impact trust. \cite{short_no_2010} also adopted a similar
pattern when introducing unexpected robot behaviour.

%
%\begin{figure}[!t]
%    \centering
%    \subfloat[lost]{
%        \label{fig:domino-lost}
%        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
%    }
%    \subfloat[disobey]{
%        \label{fig:domino-disobey}
%        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
%    }
%    \subfloat[mistake]{
%        \label{fig:domino-mistake}
%        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
%    }
%    \caption{\small The three robot misbehaviours.}
%    \label{fig:domino-misbehaviour}
%\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.6\columnwidth]{domino-disobey.png}
    \caption{\small The experimental setup, here in the \emph{disobey} condition.}
    \label{fig:domino-misbehaviour}
\end{figure}

@@

    \item \textbf{Lost:} After being called, Ranger goes until it is on the
    carpet. There, it stops, turns, and goes wrong (see blue path in
    Figure~\ref{fig:domino-setup}). Once at the wrong position, Ranger waits
    with its ``face'' turned away from the child, and it blinks in yellow light,
    as it would only do when in front of a child. Ranger remains waiting at the wrong
    position until the experimenter tells the child to go over to the robot to
    put the domino tile. The \textit{lost} behaviour is \textit{human-repaired},
    as it needs human-intervention.

    \item \textbf{Disobey:} After being called, Ranger goes until it is on the
    carpet. It then stops, makes red
    light all over its surface and produces a repeated ``disturbance'' sound. It
    turns, and goes to a wrong position (see red path in
    Figure~\ref{fig:domino-setup}). Still blinking in red, it turns its ``face''
    toward the searcher child. In addition to the red blinking, Ranger
    makes a slow wiggle-like move, and remains waiting at the wrong position
    until the experimenter tells the child to go over to the robot to put the
    domino tile. The \textit{disobey} behaviour is also \textit{human-repaired}.

    \item \textbf{Mistake:} The searcher child calls Ranger. The robot goes until
    it is on the carpet, stops, turns, and goes wrong (see yellow path in
    Figure~\ref{fig:domino-setup}). Then, Ranger waits ($\sim$2~sec), turns its
    ``face'' toward the searcher child, and ``blushes'' red around its ``cheeks''
    (as if it recognises its wrong position) and finally goes correctly over to
    the searcher child. The \textit{mistake} behaviour is \textit{robot-repaired},
    as no human-intervention is needed.

@@

On its way back to the tent, Ranger always goes correctly. After the searcher
child has put a domino tile, Ranger automatically turns and goes over to the
tent (the receiver child does not need to call the robot). The receiver child
takes the tile and the robot moves to a waiting location until the next run
starts.

\subsection{Data Collection}

We have obtained and analysed two types of data. The \textbf{children's
behaviour toward the robot} (\ie the child-robot interactions) have been
captured in the video recordings by annotating a set of actions, described
below. Children's \textbf{phenomenological perception of the robot} has been
captured through two audio-recorded semi-structured interviews which took place
between run \emph{1.5} and \emph{2.1} and at the end of the experiment. A
short preliminary interview was also conducted to explain the game and assess
the expectations of the children toward the robot.

\subsubsection{Interaction: Action Coding}

@@

We annotated children's behaviour in the video records, and coded 10 different
actions (the coding scheme has been inspired from~\cite{fink2014which}):
\textbf{explore} (actively try to find out what the robot is doing, \eg by
looking under the box; attentively watch or observe the robot; experiment with
the robot to figure out how it works); \textbf{misuse} (kick the robot, poke it
in its ``eye'', try to climb on or inside the box, drive/push the robot around,
stop the robot's wheels with a foot); \textbf{put} (a domino tile is put inside
the box); \textbf{remove} (a domino tile is removed from the box);
\textbf{gesture} (gestures are used to communicate/interact with the robot, \eg
pointing gestures, waving at the robot); \textbf{touch} (the box is touched, \eg
petted or caressed); \textbf{show} (show something to the robot); \textbf{call}
(call the robot to come over); \textbf{talk} (all the other cases of direct
verbal interaction); \textbf{look} (when a child looks \emph{at the
experimenter} due to confusion caused by the robot; look is not coded when the
experimenter asks a question to the child);

@@

The actions \textit{put, remove} and \textit{call} are ``requested'' actions
that the children had to perform in the scenario. On the contrary,
\textit{explore, misuse, gesture, touch, show, talk} and \textit{look} are
spontaneous actions that were not requested but arose in the interaction.  These
actions reflect engagement, and are the one we considered during the analysis.
Figure~\ref{fig:domino-time-active} shows the distribution of these actions over
the different runs, over the three condition.

\subsubsection{Perception: Semi-Structured Interviews}

One pre-interview and two interviews were conducted with the children.  We set
up the interviews like a casual conversation / discussion, so we did not
separate the two children in order to keep the situation natural. We used casual
and informal language adapted to the age of the children, and encouraged them to
justify their answers and tell us more details by asking, for example,
\textit{How do you know ... ?} or \textit{Tell me, what have you observed when
... ?}. We paid attention to not ``put words in children's mouth''.
Consequently, though we re-phrased and repeated some questions, we never forced
children to give an answer, and accepted when they said they would not know or
when they did not respond at all.

@@

In designing our interview script and selecting relevant questions, we took
inspiration from previous work on child-robot interaction and children's
perception of robots
\cite{kahn_jr._robotic_2006,leite_influence_2013,weiss_i_2009}. For instance, we
applied and adapted some of the \emph{constructs} and example questions from the
questionnaires used in \cite{kahn_jr._robotic_2006} and \cite{weiss_i_2009}. A
\emph{construct} addresses a specific factor (topic) that can be measured by
several questions. For instance, the construct ``cognitive connections'' (using
Flavell's terminology~\cite{flavell1988development}) considers the robot's
ability to hear and to see (perceptual skills), as attributed by the children.
The construct ``moral standing'' and the related question was taken from
\cite{kahn_jr._robotic_2006}.\footnote{According to
\cite{kahn_jr._robotic_2006}, \textit{moral} refers to considerations based
on an artifact's physical or psychological welfare, and virtue (whether the
artifact deserves care). An attribution of moral standing reflects, for
instance, that the robot engenders moral regard, is morally responsible,
blameworthy, has rights or deserves respect.} Similarly, we grouped
questions according to specific constructs that they evaluate (see
Table~\ref{tab:domino-questions}).

@@

    \item Other \textbf{anthropomorphic statements}: \textit{1 point} for anthropomorphic
        reason for Ranger's misbehaviour; \textit{2 points} for anthropomorphic reason
        for not leaving Ranger alone (\eg \textit{``It would be sad''}).

@@

\subsection{Misbehaviour Recognition and Interaction Engagement}

\paragraph{Misbehaviour Recognition}

As stated in the introduction, we had hypothesised that the \textit{disobey}
behaviour is perceived as the robot intentionally not doing what it should do.
The \textit{mistake} behaviour was intended to show that the robot can do a
mistake but is aware of it and able to repair its mistake, which should also
lead to the perception of intentionality and introspective skills.  Contrary, we expected that the
\textit{lost} condition is perceived as a malfunction or bug of the robot.  In
the second interview, after the robot had misbehaved, we asked children whether
the robot always did what they wanted it to do. Most children disagreed and said
they noticed something strange.
%However, there were some children who gave a
%positive answer, suggesting that they found the robot always did what they
%wanted it to do. This was a surprise. Had they not noticed the robot's
%misbehaviour? Why not? On one hand, we found that children sometimes gave
%contradictory replies when asked the same question twice. This is difficult to
%interpret. On the other hand, children may have a general tendency to please
%adults \cite{leite_long-term_2013}, and it could be the case that some were too
%shy to tell us that the robot did something strange.

@@

When asked why they thought the robot had not always come over to them, 4 of the
children did not reply. The remaining ones gave a variety of reasons
(Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9 of 37
replies) was that the robot is somehow \textit{unpredictable} in what it is
doing and that it could go \textit{``no matter where''}\footnote{We translated
children's answers from French to English. For some expressions the meaning
and connotation of an expression may not be the same. We understand
\textit{``partir dans tous les sens''} as ``to go off in all possible
directions'' and hence interpret this reflects viewing the robot as being
unpredictable.} because \textit{``with robots you have these kind of problems,
they do no matter what''}. 8 replies related to \textit{technical problems}
(including \textit{broken parts}), suggesting that children perceived the
misbehaviour as unintended by the robot. Two of the children who had interacted
with the disobeying robot said Ranger was \textit{angry}, which none of the
children in other conditions replied. 13 out of 26 children appeared to ascribe
intentionality precursors to Ranger explaining that it \textit{did not want to
continue} carrying domino tiles or that it \textit{``did something
silly''}\footnote{We understood \textit{``faire une bêtise''} as ``to do a silly
thing'' in the sense of making a mistake.}.

@@

\paragraph{Engagement}
In terms of \textbf{engagement}, the novelty of the robot certainly plays a role
here. The findings here do not directly address the issues
of long-term usage but concern short-term \textit{engagement}, which is a
pre-requisite for long-term usage.
